---
title: "Alcohol vs Seat choice"
author: "Hannah Vong"
date: "09/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```



Visually the plot shows a large difference between the back row and the front row and the front row.




## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```



According to the chart the back row drinks 8.5 more drinks than the middle row , drinking only 3.3 drinks per week.The front row drinks 1.7 per week.It is reasonable to assume that they are not drinking the same amount.



## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


The P value represents the chances of getting a result like we just obtained if the null hypothesis is actually true. Since the result is so small I reject the null hypothesis. We now need to try discover what is different from the other.

```{r}
plot(TukeyHSD(model1))
```


According to this chart the middle and front do not have a difference, however the front - back and the back-middle are different.
## Conclusions
In conclusion we found three different categorles. we had to use anovato determine the amount or drinks per week by the rows people sat in.
According to the chart the back row drinks 8.5 more drinks than the middle row , drinking only 3.3 drinks per week.The front row drinks 1.7 per week.It is reasonable to assume that they are not drinking the same amount.

The P value represents the chances of getting a result like we just obtained if the null hypothesis is actually true. Since the result is so small I reject the null hypothesis. We now need to try discover what is different from the other.
